A new breeding crossover approach for evolutionary algorithms

### 2023-09-14 paper.tex
Work in progress (Discussion).

        For each experiment, we ran 30 independent executions per algorithm and
        dimensions specified. We recorded the following results: best-found error average,
        standard deviation, total number of evaluations, and total elapsed time (in
        seconds). The labels used on the results of our summarized experiments tables
        are the following:

        \begin{itemize}
            \item   Error:       is the best-found error average.
            \item   St-Dev:      is the standard deviation calculated from the error. 
            \item   Evals.:      is the total number of evaluations the algorithm executed.
            \item   Time:        is the total elapsed or wall clock time, in seconds. 
        \end{itemize}

        The alternatives to restart this new population are the creation of a new set
        of candidate solutions based on either: 1. Crossing the Champion with the Elite;
        2. The mutation with uniform modification from the Elite; 3. The
        projection of the Elite towards the Champion; 4. Based on random use of the
        previous alternatives. We compared three strategies by grouping the previous
        alternatives in the following:

        \begin{itemize}
            \item   Xover Mutation:      Crossing the Champion with the Elite, and the mutation with uniform modification from the Elite.
            \item   Elite Projection:    The projection of the Elite towards the Champion. 
            \item   All Random:          Based on random use of the previous alternatives.
        \end{itemize}

        \subsubsection{Ackley Benchmark Function Experiment}

            The goal of the first experiment was to confirm that this paper’s
            proposed strategy obtained improved results over our basic
            technique, which created a new population with a random generation
            of a new set of candidate solutions. We chose Ackley as the first
            Classic Benchmark Function for Optimization to test our algorithm
            behavior, where Figure~\ref{fig.fun_ackley} shows its corresponding
            Box and Whisker chart, and we summarized the results in
            Tables~\ref{tab.fun_ackley5} and~\ref{tab.fun_ackley10} (for five 
            and ten dimensions, respectively).

            \begin{figure}
                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_ackley.pdf}
                \caption{Box and whisker chart for the Ackley Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_ackley}
                \end{figure}

            \begin{table}[]
                \scriptsize
                \centering
                \caption{Ackley Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_ackley5}
                \begin{tabular}{@{}lllll@{}}
                \toprule
                \multicolumn{5}{l}{\textbf{Ackley Function - 5 Dimensions}} \\ \midrule
                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
                \textbf{Xover Mutation} & 8.69E-08 & 1.36E-08 & 46,331 & 49.9 \\
                \textbf{Elite Projection} & 6.33E-08 & 2.70E-08 & 13,811 & 18.1 \\
                \textbf{All Random} & 6.78E-08 & 2.55E-08 & 30,236 & 32.8 \\ \bottomrule
                \end{tabular}
                \end{table}

            \begin{table}[]
                \scriptsize
                \centering
                \caption{Ackley Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_ackley10}
                \begin{tabular}{@{}lllll@{}}
                \toprule
                \multicolumn{5}{l}{\textbf{Ackley Function - 10 Dimensions}} \\ \midrule
                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
                \textbf{Xover Mutation} & 9.35E-08 & 5.93E-09 & 104,842 & 111.7 \\
                \textbf{Elite Projection} & 5.11E-08 & 3.13E-08 & 16,019 & 20.1 \\
                \textbf{All Random} & 6.89E-08 & 2.75E-08 & 43,631 & 46.3 \\ \bottomrule
                \end{tabular}
                \end{table}

@@

        \subsubsection{Bohachevsky Benchmark Function Experiment}

            As our second experiment to further validate and prove our
            algorithm behavior, we chose Bohachevsky Classic Benchmark Function
            for Optimization. Figure~\ref{fig.fun_bohachevsky} shows its
            corresponding Box and Whisker chart, where we summarized the
            results in Tables~\ref{tab.fun_bohachevsky5} and~\ref{tab.fun_bohachevsky10} 
            (for five and ten dimensions, respectively). Due to the observation 
            and analysis of these results, we identify our proposed strategy 
            obtained solutions in the same order as the traditional Xover Mutation, 
            in a significantly reduced number of evaluations.

            \begin{figure}
                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_bohachevsky.pdf}
                \caption{Box and whisker chart for the Bohachevsky Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_bohachevsky}
                \end{figure}

            \begin{table}[]
                \scriptsize
                \centering
                \caption{Bohachevsky Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_bohachevsky5}
                \begin{tabular}{@{}lllll@{}}
                \toprule
                \multicolumn{5}{l}{\textbf{Bohachevsky Function - 5 Dimensions}} \\ \midrule
                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
                \textbf{Xover Mutation} & 7.28E-08 & 2.20E-08 & 15,010 & 24.2 \\
                \textbf{Elite Projection} & 4.51E-08 & 2.94E-08 & 8,266 & 12.6 \\
                \textbf{All Random} & 6.16E-08 & 2.85E-08 & 11,998 & 21.7 \\ \bottomrule
                \end{tabular}
                \end{table}

            \begin{table}[]
                \scriptsize
                \centering
                \caption{Bohachevsky Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_bohachevsky10}
                \begin{tabular}{@{}lllll@{}}
                \toprule
                \multicolumn{5}{l}{\textbf{Bohachevsky Function - 10 Dimensions}} \\ \midrule
                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
                \textbf{Xover Mutation} & 8.66E-08 & 1.38E-08 & 40,166 & 44.4 \\
                \textbf{Elite Projection} & 3.80E-08 & 3.34E-08 & 8,506 & 12.9 \\
                \textbf{All Random} & 5.34E-08 & 3.76E-08 & 19,537 & 26.8 \\ \bottomrule
                \end{tabular}
                \end{table}

@@

        \subsubsection{Griewank Benchmark Function Experiment}

            The third experiment objective was to confirm Animal Life Cycle
            Algorithm continued finding solutions in a reduced number of
            evaluations. For this test, we selected the Griewank Benchmark
            Function for Optimization. Figure~\ref{fig.fun_griewank} shows its
            corresponding Box and Whisker chart, where we summarized the
            results in Tables~\ref{tab.fun_griewank5} and~\ref{tab.fun_griewank10} 
            (for five and ten dimensions, respectively). With this analysis, 
            we confirmed our strategy continued to obtain solutions in the same 
            order as expected, in a reduced number of evaluations and less time.

            \begin{figure}
                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_griewank.pdf}
                \caption{Box and whisker chart for the Griewank Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_griewank}
                \end{figure}

            \begin{table}[]
                \scriptsize
                \centering
                \caption{Griewank Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_griewank5}
                \begin{tabular}{@{}lllll@{}}
                \toprule
                \multicolumn{5}{l}{\textbf{Griewank Function - 5 Dimensions}} \\ \midrule
                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
                \textbf{Xover Mutation} & 6.92E-08 & 2.40E-08 & 44,566 & 48.3 \\
                \textbf{Elite Projection} & 3.77E-08 & 2.74E-08 & 16,412 & 20.1 \\
                \textbf{All Random} & 5.63E-08 & 2.99E-08 & 35,761 & 38.5 \\ \bottomrule
                \end{tabular}
                \end{table}

            \begin{table}[]
                \scriptsize
                \centering
                \caption{Griewank Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_griewank10}
                \begin{tabular}{@{}lllll@{}}
                \toprule
                \multicolumn{5}{l}{\textbf{Griewank Function - 10 Dimensions}} \\ \midrule
                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
                \textbf{Xover Mutation} & 8.07E-08 & 1.39E-08 & 92,885 & 100.0 \\
                \textbf{Elite Projection} & 4.21E-08 & 3.40E-08 & 13,534 & 17.3 \\
                \textbf{All Random} & 5.08E-08 & 3.54E-08 & 40,544 & 52.5 \\ \bottomrule
                \end{tabular}
                \end{table}

@@

        \subsubsection{Rastrigin Benchmark Function Experiment}

            This experiment's goal was to follow and study the behavior of our
            proposed strategy, to repeat the results in the same order as
            expected, in a reduced number of both time and evaluations. We
            selected Rastrigin Classic Benchmark Function for Optimization for
            this experiment. Figure~\ref{fig.fun_rastrigin} shows its
            corresponding Box and Whisker chart, where we summarized the
            results in Tables~\ref{tab.fun_rastrigin5} and~\ref{tab.fun_rastrigin10} 
            (for five and ten dimensions, respectively).

            \begin{figure}
                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_rastrigin.pdf}
                \caption{Box and whisker chart for the Rastrigin Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_rastrigin}
                \end{figure}

            \begin{table}[]
                \scriptsize
                \centering
                \caption{Rastrigin Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_rastrigin5}
                \begin{tabular}{@{}lllll@{}}
                \toprule
                \multicolumn{5}{l}{\textbf{Rastrigin Function - 5 Dimensions}} \\ \midrule
                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
                \textbf{Xover Mutation} & 7.85E-08 & 1.59E-08 & 22,322 & 34.1 \\
                \textbf{Elite Projection} & 4.42E-08 & 3.26E-08 & 10,860 & 14.8 \\
                \textbf{All Random} & 5.66E-08 & 2.81E-08 & 21,122 & 35.0 \\ \bottomrule
                \end{tabular}
                \end{table}

            \begin{table}[]
                \scriptsize
                \centering
                \caption{Rastrigin Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_rastrigin10}
                \begin{tabular}{@{}lllll@{}}
                \toprule
                \multicolumn{5}{l}{\textbf{Rastrigin Function - 10   Dimensions}} \\ \midrule
                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
                \textbf{Xover Mutation} & 8.56E-08 & 1.23E-08 & 53,579 & 58.7 \\
                \textbf{Elite Projection} & 3.17E-08 & 2.57E-08 & 8,704 & 13.0 \\
                \textbf{All Random} & 5.00E-08 & 3.16E-08 & 24,376 & 27.4 \\ \bottomrule
                \end{tabular}
                \end{table}

@@

        \subsubsection{Sphere Benchmark Function Experiment}

            For our fifth experiment we chose the Sphere Classic Benchmark
            Function for Optimization. Even though the sphere function is
            considered one of the simplest to solve, the same behavior was
            consistent for the algorithm, where it showed a reduced number of
            evaluations and execution time. We can confirm this affirmation
            with the results shown in this experiment.
            Figure~\ref{fig.fun_sphere} displays its corresponding Box and
            Whisker chart, where we summarized the results in
            Tables~\ref{tab.fun_sphere5} and~\ref{tab.fun_sphere10} (for
            five and ten dimensions, respectively).

            \begin{figure}
                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_sphere.pdf}
                \caption{Box and whisker chart for the Sphere Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_sphere}
                \end{figure}

            \begin{table}[]
                \scriptsize
                \centering
                \caption{Sphere Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_sphere5}
                \begin{tabular}{@{}lllll@{}}
                \toprule
                \multicolumn{5}{l}{\textbf{Sphere Function - 5 Dimensions}} \\ \midrule
                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
                \textbf{Xover Mutation} & 7.82E-08 & 1.65E-08 & 11,312 & 14.5 \\
                \textbf{Elite Projection} & 3.60E-08 & 3.27E-08 & 7,056 & 10.9 \\
                \textbf{All Random} & 6.14E-08 & 2.79E-08 & 9,158 & 12.2 \\ \bottomrule
                \end{tabular}
                \end{table}

            \begin{table}[]
                \scriptsize
                \centering
                \caption{Sphere Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_sphere10}
                \begin{tabular}{@{}lllll@{}}
                \toprule
                \multicolumn{5}{l}{\textbf{Sphere Function - 10 Dimensions}} \\ \midrule
                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
                \textbf{Xover Mutation} & 8.39E-08 & 1.45E-08 & 30,769 & 34.4 \\
                \textbf{Elite Projection} & 4.28E-08 & 3.06E-08 & 9,236 & 13.3 \\
                \textbf{All Random} & 5.32E-08 & 3.38E-08 & 21,465 & 26.3 \\ \bottomrule
                \end{tabular}
                \end{table}

@@

        \subsubsection{Rosenbrock Benchmark Function Experiment}

            The goal of our sixth and last experiment was to study the behavior
            of the Animal Life-Cycle Algorithm when tested with the Rosenbrock
            Benchmark Function for Optimization. From all of our previous
            evaluation functions, Rosenbrock presented the most difficult
            challenge for our algorithm. This test facilitated the
            differentiation between the three compared strategies because the
            solutions found were in different numeric order. After all tests,
            the Elite Projection proved to be the best alternative. We can
            corroborate this by analyzing Figures~\ref{fig.fun_rosenbrock_5d}
            and~\ref{fig.fun_rosenbrock_10d}, which shows its corresponding Box
            and Whisker chart. We present the summarized results in
            Tables~\ref{tab.fun_rosenbrock5} and~\ref{tab.fun_rosenbrock10}
            (for five and ten dimensions, respectively).

            \begin{figure}
                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_rosenbrock_5d.pdf}
                \caption{Box and whisker chart for the Rosenbrock Benchmark Function, 5 Dimensions.} \label{fig.fun_rosenbrock_5d}
                \end{figure}

            \begin{table}[]
                \scriptsize
                \centering
                \caption{Rosenbrock Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_rosenbrock5}
                \begin{tabular}{@{}lllll@{}}
                \toprule
                \multicolumn{5}{l}{\textbf{Rosenbrock Function - 5 Dimensions}} \\ \midrule
                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
                \textbf{Xover Mutation} & 4.65E-03 & 8.29E-03 & 500,000 & 646.4 \\
                \textbf{Elite Projection} & 9.62E-07 & 1.86E-06 & 307,878 & 427.0 \\
                \textbf{All Random} & 8.30E-06 & 1.58E-05 & 491,400 & 697.8 \\ \bottomrule
                \end{tabular}
                \end{table}

            \begin{figure}
                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_rosenbrock_10d.pdf}
                \caption{Box and whisker chart for the Rosenbrock Benchmark Function, 10 Dimensions.} \label{fig.fun_rosenbrock_10d}
                \end{figure}

            \begin{table}[]
                \scriptsize
                \centering
                \caption{Rosenbrock Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_rosenbrock10}        
                \begin{tabular}{@{}lllll@{}}
                \toprule
                \multicolumn{5}{l}{\textbf{Rosenbrock Function - 10 Dimensions}} \\ \midrule
                & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
                \textbf{Xover Mutation} & 1.35E+00 & 9.83E-01 & 1,000,000 & 1,384.3 \\
                \textbf{Elite Projection} & 4.26E-02 & 4.34E-02 & 1,000,000 & 1,146.0 \\
                \textbf{All Random} & 4.27E-02 & 6.02E-02 & 952,038 & 1,147.8 \\ \bottomrule
                \end{tabular}
                \end{table}

@@

>>>>

    \begin{figure}[!ht]
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F1x10D.pdf} 
        \end{minipage}
        \hfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F1x30D.pdf} 
        \end{minipage}
        \vfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F2x10D.pdf} 
        \end{minipage}
        \hfill
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F2x30D.pdf} 
        \end{minipage}

        \caption{Box and Whisker charts for mathematical functions F1 and F2. We display the ten and thirty-dimension charts on the left and right sides for the results accumulated in 51 runs.} \label{fig.experiment_F1-F2}
    \end{figure}

@@

    \begin{figure}[!ht]
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F3x10D.pdf} 
        \end{minipage}
        \hfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F3x30D.pdf} 
        \end{minipage}
        \vfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F4x10D.pdf} 
        \end{minipage}
        \hfill
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F4x30D.pdf} 
        \end{minipage}
        \vfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F5x10D.pdf} 
        \end{minipage}
        \hfill
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F5x30D.pdf} 
        \end{minipage}
        \vfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F6x10D.pdf} 
        \end{minipage}
        \hfill
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F6x30D.pdf} 
        \end{minipage}
        \vfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F7x10D.pdf} 
        \end{minipage}
        \hfill
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F7x30D.pdf} 
        \end{minipage}
        \vfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F8x10D.pdf} 
        \end{minipage}
        \hfill
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F8x30D.pdf} 
        \end{minipage}

        \caption{Box and Whisker charts for mathematical functions F3 to F8. We display the ten and thirty-dimension charts on the left and right sides for the results accumulated in 51 runs.} \label{fig.experiment_F3-F8}
    \end{figure}

@@

    \begin{figure}[!ht]
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F9x10D.pdf} 
        \end{minipage}
        \hfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F9x30D.pdf} 
        \end{minipage}
        \vfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F10x10D.pdf} 
        \end{minipage}
        \hfill
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F10x30D.pdf} 
        \end{minipage}
        \vfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F11x10D.pdf} 
        \end{minipage}
        \hfill
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F11x30D.pdf} 
        \end{minipage}
        \vfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F12x10D.pdf} 
        \end{minipage}
        \hfill
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F12x30D.pdf} 
        \end{minipage}
        \vfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F13x10D.pdf} 
        \end{minipage}
        \hfill
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F13x30D.pdf} 
        \end{minipage}
        \vfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F14x10D.pdf} 
        \end{minipage}
        \hfill
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F14x30D.pdf} 
        \end{minipage}

        \caption{Box and Whisker charts for mathematical functions F9 to F14. We display the ten and thirty-dimension charts on the left and right sides for the results accumulated in 51 runs.} \label{fig.experiment_F9-F14}
    \end{figure}

@@

    \begin{figure}[!ht]
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F15x10D.pdf} 
        \end{minipage}
        \hfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F15x30D.pdf} 
        \end{minipage}
        \vfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F16x10D.pdf} 
        \end{minipage}
        \hfill
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F16x30D.pdf} 
        \end{minipage}
        \vfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F17x10D.pdf} 
        \end{minipage}
        \hfill
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F17x30D.pdf} 
        \end{minipage}
        \vfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F18x10D.pdf} 
        \end{minipage}
        \hfill
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F18x30D.pdf} 
        \end{minipage}
        \vfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F19x10D.pdf} 
        \end{minipage}
        \hfill
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F19x30D.pdf} 
        \end{minipage}
        \vfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F20x10D.pdf} 
        \end{minipage}
        \hfill
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F20x30D.pdf} 
        \end{minipage}

        \caption{Box and Whisker charts for mathematical functions F15 to F20. We display the ten and thirty-dimension charts on the left and right sides for the results accumulated in 51 runs.} \label{fig.experiment_F15-F20}
    \end{figure}

@@

    \begin{figure}[!ht]
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F21x10D.pdf} 
        \end{minipage}
        \hfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F21x30D.pdf} 
        \end{minipage}
        \vfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F22x10D.pdf} 
        \end{minipage}
        \hfill
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F22x30D.pdf} 
        \end{minipage}
        \vfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F23x10D.pdf} 
        \end{minipage}
        \hfill
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F23x30D.pdf} 
        \end{minipage}
        \vfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F24x10D.pdf} 
        \end{minipage}
        \hfill
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F24x30D.pdf} 
        \end{minipage}
        \vfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F25x10D.pdf} 
        \end{minipage}
        \hfill
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F25x30D.pdf} 
        \end{minipage}
        \vfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F26x10D.pdf} 
        \end{minipage}
        \hfill
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F26x30D.pdf} 
        \end{minipage}

        \caption{Box and Whisker charts for mathematical functions F21 to F26. We display the ten and thirty-dimension charts on the left and right sides for the results accumulated in 51 runs.} \label{fig.experiment_F21-F26}
    \end{figure}

@@

    \begin{figure}[!ht]
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F27x10D.pdf} 
        \end{minipage}
        \hfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F27x30D.pdf} 
        \end{minipage}
        \vfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F28x10D.pdf} 
        \end{minipage}
        \hfill
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F28x30D.pdf} 
        \end{minipage}
        \vfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F29x10D.pdf} 
        \end{minipage}
        \hfill
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F29x30D.pdf} 
        \end{minipage}
        \vfill
        \vspace{0.05 cm}
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F30x10D.pdf} 
        \end{minipage}
        \hfill
        \begin{minipage}[h]{0.49\linewidth}
            \includegraphics[width=1\linewidth]{img/fig_experiment_F30x30D.pdf} 
        \end{minipage}

        \caption{Box and Whisker charts for mathematical functions F27 to F30. We display the ten and thirty-dimension charts on the left and right sides for the results accumulated in 51 runs.} \label{fig.experiment_F27-F30}
    \end{figure}

@@

    For each experiment, we ran fifty-one independent executions per CEC-2017 mathematical benchmark function and dimensions specified. We recorded the following results: best-found error average, standard deviation, and calculated the statistical Z-Test value. The labels used on the results of our summarized results tables are the following:

    \begin{itemize}
        \item   Fx:          is the mathematical benchmark function.
        \item   Mean:        is the best-found error average.
        \item   St-Dev:      is the standard deviation calculated from the error. 
        \item   Z:           is the calculated statistical Z-Test value.
    \end{itemize}

    To find and determine the best alternative finalized with a statistical Z-Test with a 95 percent confidence level. Here are the results statistics values: Table 3 shows the condensed ALCA evaluation results for the CEC-2017 functions running on ten dimensions (D) for alternatives One Point and Continuous Range crossover; Table 4 displays the condensed ALCA evaluation results for the CEC-2017 mathematical operations running on thirty D for the same crossover alternatives.

    We performed the statistical Z-Test for both crossover alternatives with a 95 percent confidence level. When the One Point passes the test, it is highlighted in green color. When the Continuous Range passes the statistical test, it is highlighted in blue. Where we did not find enough evidence to declare one choice as the best alternative, no Z value was highlighted.
